Scaling up the hyperparameter grid for Naomi

### 2023-04-05 src/dev_scale-grid/scale-grid.Rmd
Understanding further what is going on with the Choleksy adapted AGHQ with vector levels #22

>>>>

Verifying that there are two grid points used in the 16th dimension:

```{r}
stopifnot(nrow(quad$modesandhessians) == 2)

quad$modesandhessians[, 1:24] %>%
  pivot_longer(cols = everything()) %>%
  ggplot(aes(x = name, y = value)) +
    geom_point(alpha = 0.8) +
    labs(x = "", y = "Value") + 
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 1))
```

Note that for the Cholesky adapted grid with `levels = c(1, 1, ..., 2, 1, ..., 1)` we see variation in all of the dimensions further than the one with a level above one.
I would assume this is related in some way to the Cholesky adaption being based on a lower triangular matrix.
This is something it would be worthwhile to work out in more detail.

```{r}
diff(as.matrix(quad$modesandhessians[, 1:24]))
```

Verifying that adaption is happening as we expect it to be:

```{r}
#' This is what the base grid looks like
mvQuad::getNodes(base_grid)

#' Rescale it according to the mode and Hessian with Cholesky factor
mvQuad::rescale(base_grid, m = quad$optresults$mode, C = Matrix::forceSymmetric(solve(quad$optresults$hessian)), dec.type=2)

#' Verify that the adapted grid has the same nodes and are used by aghq::aghq
stopifnot(all(mvQuad::getNodes(base_grid) == unname(as.matrix(quad$modesandhessians[, 1:24]))))
```
